Hydras \& Co.

### 2023-06-13 doc/chapter-fol.tex

I

@@

@@

\begin{todo}
Link to folProp.v
\end{todo}

Section \texttt{Free\_Variables} 
of~\href{../theories/html/hydras.Ackermann.fol.html}{Ackermann.fol} defines the list of free variables which occur in a term (respectively in a formula).

We advise the reader to look at these functions, and limit ourselves to give a few examples.

Let us consider again the formulas \texttt{f3} and \texttt{f4} of page~\pageref{fol:examplesf1f2f3}.

The list of free variable occurrences of a formula is given by the function \texttt{freeVarFormula}. The function \texttt{close}
binds all the free variables of a formula with universal quantifiers.

\inputsnippets{FolExamples/freeVarExamples}

>>>>

@@

\subsection{Structural recursion on formulas}

\subsubsection{Free variables}
The functions \texttt{freeVarT} [resp. \texttt{freeVarTs},  and
\texttt{freeVarF}] compute the multiset (as a list with possible repetitions) of the free occurrences of variables in a term [resp. a vector of terms, a formula].

\inputsnippets{folProp/freeVarT}

\inputsnippets{folProp/freeVarF, FolExamples/freeVarEx}

Note that \texttt{freeVarF} is defined by cases over the basic connectives. In the following example, the connective \texttt{<->} is expanded into a conjunction of two implications, thus the 
list returned by \texttt{freeVarF} may contain redundancies.

\inputsnippets{FolExamples/freeVarDup}

@@
